---
output:
  md_document:
    variant: gfm
---

```{r, include=FALSE}
helper <- "vignettes/real-example-helpers.R"
source(helper)
if (!bt_real_examples_enabled()) {
  stop(
    "Render index.Rmd with BLUERTOPO_BUILD_REAL_EXAMPLES=true for the pkgdown homepage.",
    call. = FALSE
  )
}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/home-",
  fig.width = 7,
  fig.height = 5,
  dpi = 144
)
```

# bluertopo

[![R-CMD-check](https://github.com/el-cordero/bluer-topo/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/el-cordero/bluer-topo/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/el-cordero/bluer-topo/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/el-cordero/bluer-topo/actions/workflows/pkgdown.yaml)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://github.com/el-cordero/bluer-topo/blob/main/LICENSE.md)

`bluertopo` discovers, downloads, verifies, and opens National Oceanic and
Atmospheric Administration (NOAA) BlueTopo bathymetry for an area of interest
using `terra`. The package keeps source GeoTIFF and RAT sidecar files intact by
default, records query and catalog provenance, and makes native
source-resolution choices explicit.

BlueTopo is not for navigation. This package performs no vertical-datum
conversion and is not affiliated with, endorsed by, or supported by NOAA.

Reference: NOAA, [BlueTopo](https://nauticalcharts.noaa.gov/data/bluetopo.html)
and [BlueTopo specifications](https://nauticalcharts.noaa.gov/data/bluetopo_specs.html).

## New York Harbor example

```{r example-setup, include=FALSE}
library(terra)

real <- bt_real_example_setup()
real_aoi <- real$aoi
real_tiles <- real$tiles
real_manifest <- bt_real_download_assets(real)
real_bathy <- bluertopo(
  real_aoi,
  layers = "elevation",
  resolution = "native",
  coverage = "fill",
  details = TRUE,
  progress = FALSE,
  quiet = TRUE
)
```

This example demonstrates tile discovery, verified asset retrieval, and
bathymetry extraction for New York Harbor. The area includes portions of Lower
Manhattan, Governors Island, Upper New York Bay, and the East River entrance.

```{r bathy-map, echo=FALSE, fig.cap="BlueTopo bathymetry for New York Harbor, displayed with hillshade, contours, and the example-area boundary.", fig.alt="BlueTopo bathymetry for New York Harbor with hillshade, contours, and the example-area boundary."}
bt_plot_bathy_map(real_bathy$data, real_aoi, main = "New York Harbor BlueTopo bathymetry")
```

```{r example-summary, echo=FALSE}
manifest_df <- as.data.frame(real_manifest)
example_summary <- data.frame(
  `Example area` = real$place,
  `Selected tiles` = nrow(real_tiles),
  `Native resolution` = paste0(sort(unique(as.data.frame(real_tiles)$resolution_m)), " m", collapse = ", "),
  `Retrieved assets` = paste0(
    sum(manifest_df$asset_type == "geotiff"), " GeoTIFFs and ",
    sum(manifest_df$asset_type == "rat"), " RAT files"
  ),
  Verification = if (all(manifest_df$verified)) "SHA-256 verified" else "Verification incomplete",
  check.names = FALSE,
  stringsAsFactors = FALSE
)
bt_display_table(example_summary)
```

## Basic workflow

```r
library(bluertopo)
library(terra)

aoi <- vect("my_area.gpkg")
bathy <- bluertopo(aoi)
plot(bathy)
```

`sf::sf` and `sf::sfc` polygon objects with a known CRS can also be passed
directly to `bluertopo()`, `bluertopo_tiles()`, and `bluertopo_download()`.

| Function | Returns |
|:---|:---|
| `bluertopo_tiles(aoi)` | Selected tile footprints and metadata as a `terra::SpatVector` |
| `bluertopo_download(aoi, path)` | Verified source-asset records as a data frame |
| `bluertopo(aoi)` | A `terra::SpatRaster` or `terra::SpatRasterCollection` |

## Provenance workflow

```r
result <- bluertopo(aoi, details = TRUE)

result$tiles
result$downloads
result$coverage
result$provenance
```

## Examples

The [Examples tab](articles/examples.html) uses NOAA BlueTopo source tiles for
New York Harbor. Normal package tests use small synthetic fixtures so checks
remain network-free. The mixed-grid example uses a documented secondary AOI
near Key West and Boca Chica Channel because the current New York Harbor plan
is one compatible 4 m native grid.

- [Example gallery](articles/examples.html)
- [Discover tiles and coverage](articles/example-discover-tiles.html)
- [Download original assets](articles/example-download-assets.html)
- [Extract elevation with terra](articles/example-extract-elevation.html)
- [Compare resolution policies](articles/example-resolution-policies.html)
- [Mixed grids and output grid](articles/example-mixed-grids.html)
- [Layers and RAT metadata](articles/example-layers-rat.html)
