---
title: "Downloads, Cache, and Reproducibility"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Downloads, Cache, and Reproducibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

`bluertopo_download()` is for workflows where the durable deliverable is the
original NOAA BlueTopo source file set. The function preserves NOAA basenames,
keeps GeoTIFF and RAT sidecar files unmodified, verifies SHA-256 checksums by
default, and writes manifests for future auditing.

## Plan first

```{r}
plan <- bluertopo_download(
  aoi,
  path = "data/raw/bluetopo",
  coverage = "fill",
  dry_run = TRUE
)
```

Dry runs return planned assets without creating the destination directory.

## Download with verification

```{r}
manifest <- bluertopo_download(
  aoi,
  path = "data/raw/bluetopo",
  rat = TRUE,
  verify = "sha256",
  on_exists = "verify"
)
```

Each row records the tile identifier, asset type, source URL, destination path,
verification status, SHA-256 value, attempts, and timestamps. A fixed manifest
is written at the download root for convenience, and query-addressed manifest
copies are written under `manifests/` when a query hash is available.

## Existing files

`on_exists = "verify"` reuses an existing file only when verification succeeds.
`on_exists = "skip"` records a skipped file without verification. `on_exists =
"replace"` redownloads the asset.

```{r}
reused <- bluertopo_download(
  aoi,
  path = "data/raw/bluetopo",
  on_exists = "verify"
)
```

## Package cache

`bluertopo()` uses the package cache for catalog files, downloaded source
assets, and VRTs. Cache roots are marked with `.bluertopo-cache.json` before
package-owned content is written.

```{r}
bluertopo_cache_dir()
```

`bluertopo_cache_clear()` clears only the configured package cache. It refuses
unmarked directories, suspicious roots, and symlinked cache paths.

```{r}
bluertopo_cache_clear(confirm = TRUE)
```

## Concurrency and retries

Downloads are currently deterministic and single-worker. `workers = NULL` and
`workers = 1` are accepted; higher values are rejected until bounded parallel
downloads are implemented. Individual assets still use retry/backoff behavior
for transient transfer failures.

```{r}
manifest <- bluertopo_download(
  aoi,
  path = "data/raw/bluetopo",
  workers = 1,
  retries = 3
)
```
