---
title: "Discover Tiles and Coverage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Discover Tiles and Coverage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}
library(terra)

example <- bt_example_setup()
example_aoi <- example$aoi
```

Every rendered output on this page uses: **`r bt_fixture_label`**

This example shows how an AOI intersects BlueTopo-style tile footprints and how
coverage diagnostics are reported. The fixture-only
`bluertopo.allow_test_hosts = TRUE` option enables local `file://` assets; it is
not part of normal live NOAA workflows.

## Selected Tiles

```{r discover}
tiles <- bluertopo_tiles(
  example_aoi,
  resolution = "native",
  coverage = "warn",
  quiet = TRUE
)
```

```{r selected-table}
bt_display_table(bt_tile_table(tiles))
```

## Coverage Diagnostics

```{r coverage-table}
coverage <- attr(tiles, "coverage")
bt_display_table(bt_coverage_table(coverage))
```

## AOI And Selected Footprints

```{r footprint-figure, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: AOI and selected tile footprints.", fig.alt="AOI outline over selected synthetic BlueTopo tile footprints."}
bt_plot_tiles(tiles, example_aoi, main = "AOI intersection with selected tiles")
```

## Coverage Fractions

```{r coverage-bars, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: coverage fractions.", fig.alt="Bar plot of published coverage, selected coverage, selected AOI fraction, and target coverage."}
coverage_values <- unlist(coverage[c(
  "published_coverage_fraction",
  "selected_coverage_fraction",
  "selected_aoi_fraction",
  "target_coverage"
)])
barplot(
  coverage_values,
  ylim = c(0, 1),
  col = c("#8ecae6", "#90be6d", "#f9c74f", "#d00000"),
  las = 2,
  ylab = "fraction",
  main = "Coverage diagnostics"
)
abline(h = coverage$target_coverage, col = "#d00000", lwd = 2, lty = 2)
```

Coverage is geometric tile-index coverage. It is not a statement about data
quality, navigational fitness, or vertical-datum compatibility.
