---
title: "Download Original Assets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Download Original Assets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/real-example-helpers.R")) {
  "vignettes/real-example-helpers.R"
} else {
  "real-example-helpers.R"
}
source(helper)
real_mode <- bt_real_examples_enabled()
```

This page uses real NOAA BlueTopo source tiles when rendered for the public
pkgdown site. `r if (real_mode) bt_real_example_label else bt_offline_note`

This page downloads the real New York Harbor NOAA BlueTopo GeoTIFFs and RAT
sidecars, verifies SHA-256 checksums, shows the manifest, and demonstrates
reuse of already verified local files.

BlueTopo is not for navigation. No vertical-datum conversion is performed.
Example downloads are intentionally small and are cached during website builds,
but they still access NOAA public data.

## Real Example Setup

```{r setup, eval=bt_real_examples_enabled()}
real <- bt_real_example_setup()
```

## First Download

```{r download, eval=bt_real_examples_enabled()}
manifest <- bt_real_download_assets(real)
```

```{r manifest-table, eval=bt_real_examples_enabled()}
bt_display_table(bt_manifest_table(manifest))
```

## Reuse Existing Verified Files

```{r reuse, eval=bt_real_examples_enabled()}
reused <- bt_real_download_assets(real)

reuse_df <- as.data.frame(reused)
reuse_summary <- aggregate(
  verified ~ status,
  data = reuse_df,
  FUN = function(x) sum(x %in% TRUE)
)
names(reuse_summary) <- c("status", "verified_count")
reuse_summary$count <- as.integer(table(reuse_df$status)[reuse_summary$status])
reuse_summary <- reuse_summary[c("status", "count", "verified_count")]

bt_display_table(reuse_summary)
```

## Manifest Files

```{r manifest-files, eval=bt_real_examples_enabled()}
bt_display_table(bt_manifest_files_table(real$download_dir))
```

## Source Domain Summary

```{r source-domain-summary, eval=bt_real_examples_enabled()}
bt_display_table(bt_source_domain_summary(manifest))
```

## Download Status Counts

```{r status-bars, eval=bt_real_examples_enabled(), fig.cap="Actual NOAA BlueTopo source assets: SHA-256 verified download status counts.", fig.alt="Bar plot of downloaded and reused real BlueTopo asset statuses."}
status_counts <- bt_status_counts(manifest)
barplot(
  stats::setNames(status_counts$count, status_counts$status),
  col = "#005f73",
  ylab = "asset count",
  main = "First-call download statuses"
)
```

The second call reports `reused_verified` for files that already exist and still
match NOAA SHA-256 checksums. RAT sidecars are downloaded and verified with the
GeoTIFF assets.
