---
title: "Layers and RAT metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Layers and RAT metadata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/real-example-helpers.R")) {
  "vignettes/real-example-helpers.R"
} else {
  "real-example-helpers.R"
}
source(helper)
real_mode <- bt_real_examples_enabled()
```

`r if (real_mode) bt_real_example_label else bt_offline_note`

This example uses BlueTopo tiles covering New York Harbor. The workflow
demonstrates tile discovery, checksum-verified asset retrieval, and file-backed
raster access with `terra`. It opens elevation, uncertainty, and contributor
layers, then reads Raster Attribute Table (RAT) sidecars for contributor
metadata. Elevation is shown with hillshade and contours; uncertainty and
contributor IDs are plotted as their own source layers.

BlueTopo is not for navigation. No vertical-datum conversion is performed. The
contributor band contains IDs, not continuous values. Contributor IDs must not
be averaged. RAT sidecars carry contributor metadata, and `bluertopo` preserves
original RAT files.

## Example area

```{r setup, include=FALSE, eval=bt_real_examples_enabled()}
library(terra)

real <- bt_real_example_setup()
real_aoi <- real$aoi
```

## All layers

```{r all-layers, eval=bt_real_examples_enabled()}
all_layers <- bluertopo(
  real_aoi,
  layers = "all",
  coverage = "fill",
  details = TRUE,
  progress = FALSE,
  quiet = TRUE
)
```

```{r layer-table, echo=FALSE, eval=bt_real_examples_enabled()}
layer_table <- data.frame(
  layer = c("elevation", "uncertainty", "contributor"),
  `source band` = c(1L, 2L, 3L),
  meaning = c(
    "source elevation values",
    "source vertical uncertainty values",
    "categorical contributor/source IDs"
  ),
  `default resampling rule` = c(
    "bilinear only when an explicit output grid is requested",
    "bilinear only when an explicit output grid is requested; values are then resampled",
    "nearest-neighbor only; never average contributor IDs"
  ),
  check.names = FALSE
)

bt_display_table(layer_table)
```

## RAT sidecar manifest

```{r rat-manifest, echo=FALSE, eval=bt_real_examples_enabled()}
rat_manifest <- as.data.frame(all_layers$downloads)
rat_manifest <- rat_manifest[rat_manifest$asset_type == "rat", , drop = FALSE]
rat_table <- data.frame(
  tile_id = rat_manifest$tile_id,
  source_basename = rat_manifest$source_basename,
  local_path = bt_short_path(rat_manifest$local_path, keep = 4L),
  verified = rat_manifest$verified,
  actual_sha256 = bt_short_sha(rat_manifest$actual_sha256),
  stringsAsFactors = FALSE
)

bt_display_table(rat_table)
```

## Contributor lookup

```{r rat-lookup, echo=FALSE, eval=bt_real_examples_enabled()}
contributor_lookup <- bt_parse_rat(rat_manifest$local_path)
bt_display_table(contributor_lookup)
```

## Elevation

```{r elevation-plot, echo=FALSE, eval=bt_real_examples_enabled(), fig.cap="BlueTopo bathymetry for New York Harbor, displayed with hillshade, contours, and the example-area boundary.", fig.alt="BlueTopo bathymetry for New York Harbor with hillshade, contours, and the example-area boundary."}
first_grid <- bt_rasters(all_layers$data)[[1L]]
bt_plot_bathy_map(first_grid[["elevation"]], real_aoi, main = "New York Harbor elevation")
```

## Uncertainty

```{r uncertainty-plot, echo=FALSE, eval=bt_real_examples_enabled(), fig.cap="BlueTopo uncertainty for the selected New York Harbor tiles.", fig.alt="BlueTopo uncertainty raster for the selected New York Harbor tiles."}
terra::plot(first_grid[["uncertainty"]], main = "Uncertainty", col = grDevices::hcl.colors(80, "BluYl"))
terra::plot(terra::project(real_aoi, terra::crs(first_grid)), add = TRUE, border = "#d00000", lwd = 2)
```

## Contributor IDs

```{r contributor-plot, echo=FALSE, eval=bt_real_examples_enabled(), fig.cap="Contributor identifiers for the selected New York Harbor tiles.", fig.alt="BlueTopo contributor identifier raster shown with categorical colors."}
terra::plot(first_grid[["contributor"]], main = "Contributor IDs", col = hcl.colors(12, "Dark 3"))
terra::plot(terra::project(real_aoi, terra::crs(first_grid)), add = TRUE, border = "#d00000", lwd = 2)
```

Contributor values are identifiers that point into RAT metadata. They are not
continuous terrain values.
