---
title: "Discover Tiles and Coverage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Discover Tiles and Coverage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/real-example-helpers.R")) {
  "vignettes/real-example-helpers.R"
} else {
  "real-example-helpers.R"
}
source(helper)
real_mode <- bt_real_examples_enabled()
```

This page uses real NOAA BlueTopo source tiles when rendered for the public
pkgdown site. `r if (real_mode) bt_real_example_label else bt_offline_note`

BlueTopo is not for navigation. No vertical-datum conversion is performed.
Coverage is geometric tile-index coverage, not a statement about navigational
fitness, data quality, or NOAA endorsement.

## Real Example Setup

```{r setup, eval=bt_real_examples_enabled()}
library(terra)

real <- bt_real_example_setup()
real_aoi <- real$aoi
```

## Selected Tiles

```{r discover, eval=bt_real_examples_enabled()}
tiles <- bluertopo_tiles(
  real_aoi,
  resolution = "native",
  coverage = "warn",
  quiet = TRUE
)
```

```{r selected-table, eval=bt_real_examples_enabled()}
bt_display_table(bt_tile_table(tiles, include_urls = TRUE))
```

## Coverage Diagnostics

```{r coverage-table, eval=bt_real_examples_enabled()}
coverage <- attr(tiles, "coverage")
bt_display_table(bt_coverage_table(coverage))
```

## AOI And Selected Footprints

```{r footprint-figure, eval=bt_real_examples_enabled(), fig.cap="Actual NOAA BlueTopo source tiles: AOI outline over selected tile footprints colored by native resolution.", fig.alt="Real BlueTopo tile footprints selected for the example AOI."}
bt_plot_tiles(tiles, real_aoi, main = "AOI intersection with NOAA BlueTopo tiles")
```

## Coverage Fractions

```{r coverage-bars, eval=bt_real_examples_enabled(), fig.cap="Actual NOAA BlueTopo source tiles: coverage fractions for the selected AOI.", fig.alt="Bar plot of published coverage, selected coverage, selected AOI fraction, and target coverage."}
coverage_values <- unlist(coverage[c(
  "published_coverage_fraction",
  "selected_coverage_fraction",
  "selected_aoi_fraction",
  "target_coverage"
)])
barplot(
  coverage_values,
  ylim = c(0, 1),
  col = c("#8ecae6", "#90be6d", "#f9c74f", "#d00000"),
  las = 2,
  ylab = "fraction",
  main = "Coverage diagnostics"
)
abline(h = coverage$target_coverage, col = "#d00000", lwd = 2, lty = 2)
```

The selected tile table includes shortened NOAA GeoTIFF and RAT URLs so users
can see that discovery is using the live BlueTopo catalog records.
