---
title: "Mixed Grids and Output Grid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Mixed Grids and Output Grid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}
library(terra)

example <- bt_example_setup()
example_aoi <- example$aoi
```

Every rendered output on this page uses: **`r bt_fixture_label`**

Mixed native grids are preserved unless the user asks for a single output grid.
`combine = "single"` needs an explicit output grid when native grids are
incompatible. Resampled uncertainty values are not original source cells, and
contributor resampling must be nearest-neighbor.

## Native Mixed-Grid Extraction

```{r native}
native <- bluertopo(
  example_aoi,
  resolution = "native",
  coverage = "fill",
  combine = "auto",
  details = TRUE,
  progress = FALSE
)
```

```{r native-table}
native_table <- bt_raster_summary(native$data)
native_table$output_object_class <- paste(class(native$data), collapse = ", ")
native_table <- native_table[c(
  "output_object_class",
  "group_name",
  "crs",
  "resolution",
  "source_count",
  "layer_names"
)]

bt_display_table(native_table)
```

## Native Grid Footprints

```{r native-footprints, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: native grid footprints selected for the mixed-grid extraction.", fig.alt="Synthetic fixture tile footprints selected for mixed native grids."}
native_tiles <- native$tiles
bt_plot_tiles(native_tiles, example_aoi, main = "Selected mixed native grids")
```

## Explicit Single Output Grid

```{r single}
single <- suppressWarnings(bluertopo(
  example_aoi,
  resolution = "native",
  coverage = "fill",
  output_crs = "EPSG:3857",
  output_resolution = 50000,
  combine = "single",
  details = TRUE,
  progress = FALSE
))
```

```{r single-table}
single_raster <- single$data
single_table <- data.frame(
  output_object_class = paste(class(single_raster), collapse = ", "),
  crs = paste0("EPSG:", terra::crs(single_raster, describe = TRUE)$code),
  resolution = paste(round(terra::res(single_raster), 3), collapse = " x "),
  extent = paste(round(as.vector(terra::ext(single_raster)), 1), collapse = ", "),
  resampled_flag = attr(single_raster, "bluertopo_resampled") %in% TRUE,
  stringsAsFactors = FALSE
)

bt_display_table(single_table)
```

```{r output-raster, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: elevation resampled onto an explicit output grid.", fig.alt="Synthetic fixture elevation raster on one explicit output grid."}
terra::plot(single$data, main = "Explicit output grid elevation")
```

The explicit grid is useful for workflows that require one raster, but it is a
resampling operation. Native source-resolution selection remains separate from
output-grid creation.
