---
title: "Download Original Assets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Download Original Assets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}

example <- bt_example_setup()
example_aoi <- example$aoi
example_download_dir <- file.path(tempdir(), "bluertopo-example-download-assets")
unlink(example_download_dir, recursive = TRUE, force = TRUE)
```

Every rendered output on this page uses: **`r bt_fixture_label`**

`bluertopo_download()` preserves original GeoTIFF and RAT sidecar files and
verifies them with SHA-256 checksums. This page uses local fixture files, not
live NOAA downloads.

## First Download

```{r download}
manifest <- bluertopo_download(
  example_aoi,
  path = example_download_dir,
  coverage = "fill",
  rat = TRUE,
  verify = "sha256",
  progress = FALSE
)
```

```{r manifest-table}
bt_display_table(bt_manifest_table(manifest))
```

## Reuse Existing Verified Files

```{r reuse}
reused <- bluertopo_download(
  example_aoi,
  path = example_download_dir,
  coverage = "fill",
  rat = TRUE,
  verify = "sha256",
  progress = FALSE
)

reuse_df <- as.data.frame(reused)
reuse_summary <- aggregate(
  verified ~ status,
  data = reuse_df,
  FUN = function(x) sum(x %in% TRUE)
)
names(reuse_summary) <- c("status", "verified_count")
reuse_summary$count <- as.integer(table(reuse_df$status)[reuse_summary$status])
reuse_summary <- reuse_summary[c("status", "count", "verified_count")]

bt_display_table(reuse_summary)
```

## Manifest Files

```{r manifest-files}
manifest_files <- list.files(
  example_download_dir,
  pattern = "manifest\\.(csv|json)$|manifest-[A-Za-z0-9]+\\.(csv|json)$",
  recursive = TRUE,
  full.names = TRUE
)
manifest_file_table <- data.frame(
  file = bt_short_path(manifest_files, keep = 3L),
  exists = file.exists(manifest_files),
  bytes = as.integer(file.info(manifest_files)$size),
  stringsAsFactors = FALSE
)

bt_display_table(manifest_file_table)
```

## Download Status Counts

```{r status-bars, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: verified download status counts.", fig.alt="Bar plot of downloaded asset status counts from the synthetic fixture."}
status_counts <- bt_status_counts(manifest)
barplot(
  stats::setNames(status_counts$count, status_counts$status),
  col = "#005f73",
  ylab = "asset count",
  main = "First-call download statuses"
)
```

The second call reports `reused_verified` for files that already exist and still
match the expected SHA-256 checksums.
