---
title: "Compare Resolution Policies"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Compare Resolution Policies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 5)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}
library(terra)

example <- bt_example_setup()
example_aoi <- example$aoi
```

Every rendered output on this page uses: **`r bt_fixture_label`**

Smaller meter values mean finer native source resolution. `resolution` selects
source tiles; it does not resample. `coverage = "fill"` can add fallback source
tiles. `output_resolution` is the argument that changes the output grid.

## Policies

```{r policies}
policies <- list(
  native = list(resolution = "native", coverage = "warn"),
  finest = list(resolution = "finest", coverage = "ignore"),
  `finest + coverage fill` = list(resolution = "finest", coverage = "fill"),
  coarsest = list(resolution = "coarsest", coverage = "ignore"),
  `exact 8 m` = list(resolution = 8, coverage = "ignore"),
  `nearest 6 m` = list(resolution = bluertopo_resolution("nearest", value = 6), coverage = "ignore")
)

policy_tiles <- lapply(policies, function(policy) {
  bluertopo_tiles(
    example_aoi,
    resolution = policy$resolution,
    coverage = policy$coverage,
    quiet = TRUE
  )
})

policy_summary <- do.call(rbind, lapply(names(policy_tiles), function(name) {
  tiles <- policy_tiles[[name]]
  df <- as.data.frame(tiles)
  coverage <- attr(tiles, "coverage")
  data.frame(
    policy = name,
    selected_tile_count = nrow(df),
    selected_resolutions = paste(sort(unique(df$resolution_m)), collapse = ", "),
    selected_coverage_fraction = coverage$selected_coverage_fraction,
    selected_aoi_fraction = coverage$selected_aoi_fraction,
    target_met = coverage$target_met,
    stringsAsFactors = FALSE
  )
}))

bt_display_table(policy_summary)
```

## Tile Selection Maps

```{r policy-maps, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: selected tiles under different native source-resolution policies.", fig.alt="Six maps showing tile selections for native, finest, coverage fill, coarsest, exact, and nearest policies."}
old_par <- par(mfrow = c(2, 3), mar = c(2, 2, 3, 1))
for (name in names(policy_tiles)) {
  bt_plot_tiles(policy_tiles[[name]], example_aoi, main = name)
}
par(old_par)
```

## Coverage By Policy

```{r policy-coverage-bars, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: selected coverage fraction by resolution policy.", fig.alt="Bar plot comparing selected coverage fractions by native source-resolution policy."}
barplot(
  stats::setNames(policy_summary$selected_coverage_fraction, policy_summary$policy),
  ylim = c(0, 1),
  las = 2,
  col = "#005f73",
  ylab = "selected coverage fraction",
  main = "Coverage by resolution policy"
)
abline(h = 1, col = "#d00000", lwd = 2, lty = 2)
```

Use an explicit output grid only when resampling is intended.
