---
title: "Layers and RAT Metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Layers and RAT Metadata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}
library(terra)

example <- bt_example_setup()
example_aoi <- example$aoi
```

Every rendered output on this page uses: **`r bt_fixture_label`**

The contributor band contains IDs, not continuous values. Contributor IDs must
not be averaged. RAT sidecars carry contributor metadata, and `bluertopo`
preserves original RAT files.

## All Layers

```{r all-layers}
all_layers <- bluertopo(
  example_aoi,
  layers = "all",
  coverage = "fill",
  details = TRUE,
  progress = FALSE
)
```

```{r layer-table}
layer_table <- data.frame(
  layer = c("elevation", "uncertainty", "contributor"),
  `source band` = c(1L, 2L, 3L),
  meaning = c(
    "source elevation values",
    "source vertical uncertainty values",
    "categorical contributor/source IDs"
  ),
  `resampling rule` = c(
    "bilinear only when an explicit output grid is requested",
    "bilinear only when an explicit output grid is requested; values are then resampled",
    "nearest-neighbor only; never average contributor IDs"
  ),
  check.names = FALSE
)

bt_display_table(layer_table)
```

## RAT Sidecar Manifest

```{r rat-manifest}
rat_manifest <- as.data.frame(all_layers$downloads)
rat_manifest <- rat_manifest[rat_manifest$asset_type == "rat", , drop = FALSE]
rat_table <- data.frame(
  tile_id = rat_manifest$tile_id,
  source_basename = rat_manifest$source_basename,
  local_path = bt_short_path(rat_manifest$local_path, keep = 4L),
  verified = rat_manifest$verified,
  actual_sha256 = bt_short_sha(rat_manifest$actual_sha256),
  stringsAsFactors = FALSE
)

bt_display_table(rat_table)
```

## Contributor Lookup

```{r rat-lookup}
contributor_lookup <- bt_parse_rat(rat_manifest$local_path)
bt_display_table(contributor_lookup)
```

## Elevation

```{r elevation-plot, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: elevation layer.", fig.alt="Synthetic fixture elevation raster."}
first_grid <- bt_rasters(all_layers$data)[[1L]]
terra::plot(first_grid[["elevation"]], main = "Elevation")
```

## Uncertainty

```{r uncertainty-plot, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: uncertainty layer.", fig.alt="Synthetic fixture uncertainty raster."}
terra::plot(first_grid[["uncertainty"]], main = "Uncertainty")
```

## Contributor IDs

```{r contributor-plot, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: contributor ID layer.", fig.alt="Synthetic fixture contributor ID raster."}
terra::plot(first_grid[["contributor"]], main = "Contributor IDs")
```

These sidecars are synthetic and compact, but they demonstrate the package
boundary: original RAT files are verified and preserved, while interpretation of
contributor IDs remains a metadata step.
