---
title: "Example Gallery"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}
library(terra)

example <- bt_example_setup()
example_root <- example$root
example_catalog <- example$catalog
example_aoi <- example$aoi
```

Every rendered output on this page uses: **`r bt_fixture_label`**

BlueTopo is not for navigation. `bluertopo` performs no vertical-datum
conversion. `resolution` selects native source tiles; `output_resolution`
resamples onto an explicit output grid.

## What The Examples Show

```{r gallery-table}
gallery <- data.frame(
  Example = c(
    "Discover tiles and coverage",
    "Download original assets",
    "Extract elevation with terra",
    "Compare resolution policies",
    "Mixed grids and output grid",
    "Layers and RAT metadata"
  ),
  `Main function` = c(
    "bluertopo_tiles()",
    "bluertopo_download()",
    "bluertopo()",
    "bluertopo_tiles()",
    "bluertopo()",
    "bluertopo()"
  ),
  Shows = c(
    "AOI intersection, selected footprints, coverage diagnostics",
    "Verified original GeoTIFF and RAT sidecar assets",
    "File-backed terra object and provenance",
    "Native source-resolution selection effects",
    "SpatRasterCollection versus explicit output grid",
    "Elevation, uncertainty, contributor IDs, and RAT metadata"
  ),
  `Output type` = c(
    "Tables and footprint figure",
    "Manifest tables and status figure",
    "terra summary tables and raster figure",
    "Policy comparison tables and maps",
    "Grid summary tables and raster figure",
    "Layer/RAT tables and raster figures"
  ),
  check.names = FALSE
)

bt_display_table(gallery)
```

## Fixture Tile Footprints

```{r tile-footprints, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: AOI outline and tile footprints by native source resolution.", fig.alt="Synthetic fixture AOI outline over three BlueTopo-style tile footprints colored by native source resolution."}
tiles <- bluertopo_tiles(example_aoi, coverage = "fill", quiet = TRUE)
bt_plot_tiles(tiles, example_aoi, main = "Synthetic fixture tile footprints")
```

```{r selected-tiles}
tiles_df <- as.data.frame(tiles)
bt_display_table(
  tiles_df[c("tile_id", "resolution_m", "utm_zone", "selection_reason", "fallback")]
)
```

## Terra Preview

```{r terra-preview, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: elevation raster preview from one source tile.", fig.alt="Small synthetic elevation raster preview from the packaged fixture."}
preview <- bluertopo(
  example_aoi,
  layers = "elevation",
  resolution = 4,
  coverage = "ignore",
  details = TRUE,
  progress = FALSE
)

terra::plot(preview$data, main = "Synthetic fixture elevation")
```

The preview is intentionally small and local. It proves the package workflow
without downloading NOAA data during documentation builds.
