---
title: "Example Gallery"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/real-example-helpers.R")) {
  "vignettes/real-example-helpers.R"
} else {
  "real-example-helpers.R"
}
source(helper)
real_mode <- bt_real_examples_enabled()
```

This page uses real NOAA BlueTopo source tiles when rendered for the public
pkgdown site. `r if (real_mode) bt_real_example_label else bt_offline_note`

This gallery downloads two real NOAA BlueTopo tiles for New York Harbor,
verifies the GeoTIFF and RAT checksums, opens the elevation band with `terra`,
and renders a hillshaded bathymetry map with contour lines.

BlueTopo is not for navigation. `bluertopo` performs no vertical-datum
conversion. The example downloads are intentionally small. Normal package tests
use synthetic fixtures; the public site uses real data. `bluertopo` is not
affiliated with, endorsed by, or supported by NOAA.

## What The Examples Show

```{r gallery-table}
gallery <- data.frame(
  Example = c(
    "Discover tiles and coverage",
    "Download original assets",
    "Extract elevation with terra",
    "Compare resolution policies",
    "Mixed grids and output grid",
    "Layers and RAT metadata"
  ),
  `Main function` = c(
    "bluertopo_tiles()",
    "bluertopo_download()",
    "bluertopo()",
    "bluertopo_tiles()",
    "bluertopo()",
    "bluertopo()"
  ),
  Shows = c(
    "AOI intersection, selected footprints, coverage diagnostics",
    "Verified NOAA GeoTIFF and RAT sidecar assets",
    "File-backed terra object and provenance",
    "Native source-resolution selection effects",
    "SpatRasterCollection versus explicit output grid",
    "Elevation, uncertainty, contributor IDs, and RAT metadata"
  ),
  `Output type` = c(
    "Tables and footprint figure",
    "Manifest tables and status figure",
    "terra summary tables and raster figure",
    "Policy comparison tables and maps",
    "Grid summary tables and raster figure",
    "Layer/RAT tables and raster figures"
  ),
  check.names = FALSE
)

bt_display_table(gallery)
```

## Real Example Setup

```{r real-setup, eval=bt_real_examples_enabled()}
library(terra)

real <- bt_real_example_setup()
real_aoi <- real$aoi
real_tiles <- real$tiles
```

## Locator Map

```{r tile-footprints, eval=bt_real_examples_enabled(), fig.cap="Actual NOAA BlueTopo source tiles: AOI outline and selected tile footprints by native source resolution.", fig.alt="Real BlueTopo tile footprints colored by native source resolution with the example AOI outline."}
bt_plot_locator_map(
  real_tiles,
  real_aoi,
  place_label = real$place,
  main = "New York Harbor real BlueTopo tile footprints"
)
```

```{r selected-tiles, eval=bt_real_examples_enabled()}
bt_display_table(bt_tile_table(real_tiles, include_urls = TRUE))
```

## Download Plan

```{r planned-assets, eval=bt_real_examples_enabled()}
planned <- real$planned_assets
planned$planned_mb <- bt_bytes_mb(planned$planned_bytes)
bt_display_table(planned[c("tile_id", "asset_type", "source_basename", "planned_mb")])
```

## Terra Preview

```{r terra-preview, eval=bt_real_examples_enabled(), fig.cap="Actual NOAA BlueTopo source data: New York Harbor elevation with hillshade, contours, and AOI outline.", fig.alt="Hillshaded real NOAA BlueTopo elevation raster with contours for New York Harbor."}
preview <- bluertopo(
  real_aoi,
  layers = "elevation",
  resolution = "native",
  coverage = "fill",
  details = TRUE,
  progress = FALSE,
  quiet = TRUE
)

bt_plot_bathy_map(preview$data, real_aoi, main = "New York Harbor NOAA BlueTopo bathymetry")
```

`resolution` selects native source tiles. `output_resolution` is used only when
the user explicitly requests an output grid.
