---
title: "Extract Elevation with terra"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extract Elevation with terra}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 6, fig.height = 4)
helper <- if (file.exists("vignettes/example-helpers.R")) {
  "vignettes/example-helpers.R"
} else {
  "example-helpers.R"
}
source(helper)
```

```{r setup}
library(terra)

example <- bt_example_setup()
example_aoi <- example$aoi
```

Every rendered output on this page uses: **`r bt_fixture_label`**

`bluertopo()` returns terra objects and, with `details = TRUE`, exposes selected
tiles, downloads, query metadata, provenance, and coverage diagnostics. Normal
native extraction does not intentionally resample.

## Extract Elevation

```{r extract}
result <- bluertopo(
  example_aoi,
  layers = "elevation",
  resolution = "native",
  coverage = "fill",
  details = TRUE,
  progress = FALSE
)
```

## Object Summary

```{r object-summary}
rasters <- bt_rasters(result$data)
object_summary <- data.frame(
  element = c(
    "result$data class",
    "number of layers",
    "layer names",
    "CRS summary",
    "resolution",
    "source count"
  ),
  class = c(
    paste(class(result$data), collapse = ", "),
    "integer",
    "character",
    "character",
    "character",
    "integer"
  ),
  value = c(
    paste(class(result$data), collapse = ", "),
    sum(vapply(rasters, terra::nlyr, numeric(1L))),
    paste(unique(unlist(lapply(rasters, names), use.names = FALSE)), collapse = ", "),
    paste(unique(vapply(rasters, function(r) as.character(terra::crs(r, describe = TRUE)$code), "")), collapse = ", "),
    paste(unique(vapply(rasters, function(r) paste(round(terra::res(r), 3), collapse = " x "), "")), collapse = "; "),
    length(unique(unlist(lapply(rasters, terra::sources), use.names = FALSE)))
  ),
  stringsAsFactors = FALSE
)

bt_display_table(object_summary)
```

## File-Backed Sources

```{r source-table}
bt_display_table(bt_sources_table(result$data))
```

## Coverage

```{r coverage-table}
bt_display_table(bt_coverage_table(result$coverage))
```

## Elevation Preview

```{r elevation-figure, fig.cap="Synthetic miniature BlueTopo fixture for package demonstration: elevation raster from the first native grid.", fig.alt="Synthetic fixture elevation raster with AOI outline."}
preview_raster <- bt_plot_first_raster(result$data, main = "Synthetic fixture elevation")
aoi_projected <- terra::project(example_aoi, terra::crs(preview_raster))
terra::plot(aoi_projected, add = TRUE, border = "#d00000", lwd = 2)
```

When native source grids differ, the result can be a `SpatRasterCollection`.
Each member can still be file-backed by verified original assets.
