---
title: "Get BlueTopo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get BlueTopo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

`bluertopo()` is the main workflow for opening NOAA BlueTopo source bathymetry
with `terra`. It discovers the current BlueTopo tile-scheme catalog, intersects
that catalog with an area of interest, downloads verified original source files
when needed, and returns file-backed `terra` rasters.

BlueTopo is not for navigation. `bluertopo` performs no vertical-datum
conversion and is not affiliated with, endorsed by, or supported by NOAA.

Reference: NOAA, [BlueTopo](https://nauticalcharts.noaa.gov/data/bluetopo.html).

## Define an AOI

Use a `terra::SpatVector`, `sf` object, bbox vector, WKT string, GeoJSON string,
or a local vector file path. Remote AOI URLs are intentionally refused.

```{r}
library(bluertopo)
library(terra)

aoi <- vect("project_area.gpkg")

# Or a bbox: c(xmin, ymin, xmax, ymax) in EPSG:4326.
aoi <- c(-66.2, 18.2, -66.1, 18.3)
```

## Discover tiles first

Inspect tile choices before downloading large GeoTIFFs.

```{r}
tiles <- bluertopo_tiles(
  aoi,
  resolution = "native",
  coverage = "warn"
)

as.data.frame(tiles)[
  c("tile_id", "resolution_m", "delivered_date", "selection_reason")
]
```

## Open bathymetry

By default, `bluertopo()` downloads original NOAA assets into the package cache,
verifies SHA-256 checksums, and opens the elevation band.

```{r}
bathy <- bluertopo(
  aoi,
  layers = "elevation",
  resolution = "native",
  coverage = "warn",
  details = TRUE
)

bathy$data
bathy$downloads
bathy$coverage
```

Set `details = TRUE` when provenance matters. The result includes selected
tiles, download statuses, query metadata, coverage diagnostics, and catalog
provenance.

## Choose layers

BlueTopo source GeoTIFFs currently expose elevation, vertical uncertainty, and
contributor/source identifier bands.

```{r}
all_layers <- bluertopo(
  aoi,
  layers = "all",
  coverage = "fill"
)
```

## Avoid accidental resampling

Native BlueTopo tiles may differ in CRS, resolution, origin, or alignment. When
selected source grids are incompatible, `bluertopo()` returns a
`terra::SpatRasterCollection` rather than silently resampling.

Request a single output grid only when resampling is an intentional analytical
choice.

```{r}
bathy_10m <- bluertopo(
  aoi,
  resolution = "native",
  output_crs = "EPSG:26918",
  output_resolution = 10,
  combine = "single"
)
```
