---
title: "Layers, contributor values, and RAT metadata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Layers, contributor values, and RAT metadata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

BlueTopo source GeoTIFFs currently include elevation, vertical uncertainty, and
contributor/source identifier bands. `bluertopo` exposes those as canonical
layer names.

## Elevation only

```{r}
elevation <- bluertopo(
  aoi,
  layers = "elevation"
)
```

## All canonical layers

```{r}
all_layers <- bluertopo(
  aoi,
  layers = "all",
  details = TRUE
)

names(all_layers$data)
```

The contributor band contains numeric identifiers. Interpret those identifiers
with the NOAA RAT sidecar metadata and source documentation. `bluertopo` can
download RAT sidecars with the original assets, but it does not currently
normalize contributor tables into a package-level lookup.

NOAA's BlueTopo product page is the package's primary external reference:
<https://nauticalcharts.noaa.gov/data/bluetopo.html>.

```{r}
assets <- bluertopo_download(
  aoi,
  path = "data/raw/bluetopo",
  rat = TRUE
)

subset(assets, asset_type == "rat")
```

## Vertical-reference metadata

`bluertopo(details = TRUE)` includes vertical-reference text discovered by
`terra`/GDAL metadata inspection when available. This is provenance text, not a
datum conversion.

```{r}
result <- bluertopo(aoi, details = TRUE)
result$provenance$vertical_reference_text
result$provenance$no_vertical_datum_conversion_performed
```

Use a domain-appropriate vertical-datum transformation outside `bluertopo` when
an analysis requires one.
